Clustering Analysis of Mobility Data

### 2018-07-06 dokumentation/data_findings.tex
fighting against motivation loss. Add first sentences

Since the data has both categorical and numerical values, the mixed euclidian distance is used as similarity measure to calculate the difference between two data points with both numerical and categorical attributes.

\subsubsection*{Mixed Euclidian Distance}
The Euclidian distance for numerical vectors is given by
$$d(p,q) = \sqrt{(p_1-q_1)^2+...+(p_n-q_n)^2} \text{ with }p=(p_1,...,p_n) \text{and }q=(q_1,...,q_n)$$
which can be extended to measure the similarity of mixed vectors with both numerical and categorical types by defining
$$(p_i-q_i)^2 = \begin{cases}
0,& \text{if } p_i=q_i\\
1,& \text{otherwise}\\
\end{cases}$$ as distance between two categorical values.

\begin{enumerate}

	\item Exponential distribution of travels regarding traveling distance\\\\

	\includegraphics[width=0.5\textwidth]{data_findings/exponential distr.png}
\end{enumerate}

>>>>

%Since the data has both categorical and numerical values, the mixed euclidian distance is used as similarity measure to calculate the difference between two data points with both numerical and categorical attributes.
%
%\subsubsection*{Mixed Euclidian Distance}
%The Euclidian distance for numerical vectors is given by
%$$d(p,q) = \sqrt{(p_1-q_1)^2+...+(p_n-q_n)^2} \text{ with }p=(p_1,...,p_n) \text{and }q=(q_1,...,q_n)$$
%which can be extended to measure the similarity of mixed vectors with both numerical and categorical types by defining
%$$(p_i-q_i)^2 = \begin{cases}
%0,& \text{if } p_i=q_i\\
%1,& \text{otherwise}\\
%\end{cases}$$ as distance between two categorical values.

\subsection*{Data Analysis}
\begin{minipage}[c]{0.48\textwidth}
\begin{figure}[H]
	\centering

		\centering
		\includegraphics[width=3.0in]{../Martin-RapidMiner/diagramme/strata_age_reasonLearnWorkRetire.png}
		\caption{Reason for movement of people at different ages grouped by strata}
		\label{fig:strata_reason_age}

\end{figure}
	\end{minipage}
\begin{minipage}{0.48\textwidth}
	We are looking for clusters inside the whole dataset by generating different charts which visualize a subset of attributes of all data points. Firstly, before neglecting the strata data of the data set, we consider chart \ref{fig:strata_reason_age} which visualizes the different reasons why people move at which age grouped by socio-economic classes. Throughout the classes each cloud of points is very similar, i. e. young people are mostly studying, adults are mostly working and older people are moving for recreation or health. Therefore categorizing people by taking the reason for their movements into account is not an option. The only difference that is not caused by outliers is the smaller size of the first and last economic class.

\end{minipage}

%\begin{enumerate}

%	\item Exponential distribution of travels regarding traveling distance\\\\

%	\includegraphics[width=0.5\textwidth]{data_findings/exponential distr.png}
%\end{enumerate}
